--------------------
title: "P8105 - HW I"
author: Pavithra Srinivasan
date: September 20, 2023
output: github_document
--------------------

```{r,setup}
library(moderndive)
library(tidyverse)
```
Loading the data set
```{r}
data("early_january_weather")

```
## Problem 1: 

Data set description: The sample size is 358, and describes the temperature, 
humidity, and wind pattern/speed during early January in the year 2013. 

```{r}
## Size of the data set
early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)

## Using pull to take the mean of the temp. 
mean(pull(early_january_weather, temp))
```
Creating a scatter plot:

```{r}
plot_df = tibble(
  x = "time_hour",
  y = "temp"
)
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()

```

The scatter plot shows a positive correlation between temperature and humidity.
As temperature increases, the humidity also increases with it. There is a
positive correlation with time and temperature as well. Temperatures rise during
the day and decrease at night time by the hour. 

ggsave("scatter_plot.pdf", height = 4, width = 4)

## Problem 2

Creating a data-frame

```{r}
plot_df = tibble(
  sample = rnorm(10),
  sample_ii = sample > 0,
  vec_character_length = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
  vec_factor = factor(c("low", "low", "low", "avg", "avg", "avg", "avg", "high", "high", "high"))
)
```

Taking the mean of each element of the data frame:
```{r}
mean(plot_df[["sample"]])
mean(plot_df[["sample_ii"]])
mean(plot_df[["vec_character_length"]])
mean(plot_df[["vec_factor"]])
```

Taking the mean works for all the elements except for `vector character length` and `vector factor`because they are character variables and not numeric. . 

Writing a code chunk using as.numeric to convert character variables into numeric. 

```{r}
logical = as.numeric(plot_df[["sample"]])
character = as.numeric(plot_df[["vec_character_length"]])
Factor = as.numeric(plot_df[["vec_factor"]])

```

Taking the mean of them again to test if the as.numeric function worked: 
```{r}
mean(logical)
mean(character)
mean(factor)
```

Both the logical and character variables yielded a numerical mean value, and the vector variable yielded a "NA" because I particularly assigned them non-numerical categories that ranged "low" "avg" and "high". 



