--------------------
title: "P8105 - HW I"
author: Pavithra Srinivasan
date: September 20, 2023
output: github_document
--------------------

```{r,setup}
library(moderndive)
library(tidyverse)
```
Loading the data set
```{r}
data("early_january_weather")

```
## Problem 1: 

Data set description: The sample size is 358, and describes the temperature, 
humidity, and wind pattern/speed during early January in the year 2013. 

```{r}
## Size of the data set
early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)

## Using pull to take the mean of the temp. 
mean(pull(early_january_weather, temp))
```
Creating a scatter plot:

```{r}
plot_df = tibble(
  x = "time_hour",
  y = "temp"
)
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()

```
The scatter plot shows a positive correlation between tempeature and humidity. As temperature increases, the humidity also increases with it. There is a positive correlation with time and temperature. Temperatures rise through during the day and decrease at night time by the hour. 

ggsave("scatter_plot.pdf", height = 4, width = 4)

## Problem 2
